Beyond Adaptive Web Design

### 2014-02-19 paper/paper.tex
refactor(): rewrite Introduction

The basic approach how to provide an optimal viewing experience is to use Responsive web design which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}. While creating flexible layouts is important, there's a lot more that goes into truly exceptional adaptive web experiences. The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.

The power of the web is its ubiquity. No one knows what the landscape is going to look like in a couple years, but there's a good chance the new devices in a few years from now will have access to the web. Because of this, we need to preserve and embrace the web's ubiquity. This requires us to deliver full web experiences regardless of how and where people access the web. It's important to continue creating flexible interfaces that can adapt to any screen size. Performance often takes a back seat to everything else. Progressive enhancement, feature detection and many other techniques allow us to build up a core experience that allow us to support more devices while still optimizing for the the best of the best. The key aspect of Future Friendly thinking is to acknowledge and embrace unpredictability. Nobody knows where things are going but the one thing we can count on is the evolution.

Adaptive web design is essentially progressive enhancement at its core, but it's being applied to a much larger, more diverse landscape than when the term progressive enhancement was first coined. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. We also have many types of internet connections with different qualities.

Responsive design is one technique in an adaptive web design strategy. Creating flexible layouts is extremely important, but it's just one piece of the puzzle. It's also important to consider a whole host of other factors as well: ergonomics, touch capability and other input methods, internet connection, geolocation and many other features that can be detected.

We consider ``adaptive web design'' as a synonym with creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access superpowers in devices.

>>>>

The basic approach how to provide an optimal viewing experience is to use ``Responsive web design'' which comes with fluid grids, flexible images and CSS3 media queries~\cite{responsive}. While creating flexible layouts is important, there's a lot more that requires exceptional adaptive web experiences. The principles of Adaptive Design are: ubiquity, flexibility, performance, enhancement and future-friendliness~\cite{adaptivesxsw}.

The power of the web is its ubiquity. No one knows what the landscape is going to appear in a couple years, but there's a reasoneable probability the new devices in a few years from now will have access to the web. Because of this, we need to preserve and embrace the web's ubiquity. This requires us to provide full web experiences regardless of how and where people access the web. It's important to remain in creating flexible interfaces that can adapt to any screen size. Performance is often less important to everything else. ``Progressive enhancement'', feature detection and many other techniques allow us to increase experience that allow us to support more devices while still optimizing for the finest. The key aspect of ``Future Friendly'' thinking is to acknowledge and embrace unpredictability. Nobody knows where things are going but the one thing we can trust is the evolution.

Adaptive web design is fundamentally progressive enhancement, but it's being applied to a much larger and more diverse landscape. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. We also have many types of internet networks with different speed, latency and quality. Responsive design is also one technique in an adaptive web design strategy. Creating flexible layouts is important, but there are many more factors we need to think about. It's also important to consider as well ergonomics, touch capability, other input methods, internet connections and many other features that can be detected.

We consider ``adaptive web design'' as a equal to creating a single Web experience that modifies based on the capabilities of the device and browser. Website can access sensors in devices and use them to enhance user experience.
